
This thesis would not have happened without the help and generosity of many people.

First and foremost, thanks to Brig Williams and Ryan Reece, my advisor and mentor, respectively. I have learned a fantastic amount of physics from you, and I hope I can be helpful to others in the same ways you've been helpful to me.

Thanks to my friends at Penn with whom I worked through classes, including Kurt Brendlinger, Jamie Saxon, Matt Hickman, and Sam Schoenholz. Our time in the Zoo was incredibly fun, and I'm happy to have grown up as a physicist with you.

Thanks to the Penn professors on ATLAS: Brig Williams, Joe Kroll, Evelyn Thomson, and Elliot Lipeles. You've been outstanding caretakers of the Penn Army. I'm sure the group will continue to flourish under your leadership for many years to come. Thanks also to Paul Keener, whose tireless stewardship of the Penn computing cluster aided in much of the work in this thesis.

Thanks to the analyzers from $\Zptautau$, including Will Davey, Andres Florez, Andrew Leister, Gabriel Palacino, Ryan Reece, and Peter Wagner. Thanks especially to Ryan and Will, with whom I worked closely. This was my introduction to ATLAS, and it could not have been more fun.

Thanks to the conveners of tau performance, including Soshi Tsuno, Stan Lai, Stefania Xella, Martin Flechl, Will Davey, and Attilio Andreazza, who helped coordinate a great collection of tau enthusiasts and authored many lovely e-mails. Your feedback and insight was invaluable.

Thanks to the analyzers from $\Htautau$ with whom I had the joy of interacting with regularly, including Swagato Banerjee, Quentin Buat, Sofia Consonni, Noel Dawe, Lidia Dell-Asta, Pier-Olivier DeViveiros, Katy Grimm, Keita Hanawa, Louis Helary, Carl Jeske, Koji Nakamura, Henrik Ohman, Nils Ruthmann, Yuki Sakurai, and Michel Trottier-McDonald. Thanks especially to Nils, with whom I worked closely. Thanks to the $\Htautau$ conveners, including Sasha Pranko, Stan Lai, Elias Coniavitis, Sinead Farrington and Luca Fiorini, for helping lead our group to a fantastic publication. Thanks also to the Higgs prospectors, including Olivier Arnaez, Jonathan Long, Leandro Nisanti, Richard Polifka, and Doug Schaefer. Thanks to the entire ATLAS collaboration for operating such an incredible experiment.

Thanks to all the students on ATLAS who wrote theses before me, especially John Alison, Mike Hance, Sarah Heim, Josh Kunkle, Larry Lee, Chris Lester, Chris Meyer, Dominick Olivito, Ryan Reece, Nils Ruthmann, Jamie Saxon, Doug Schaefer, and Jon Stahlman. You helped shape the structure and content of this thesis.

Thanks to the many friends I've made in grad school, especially John Alison, Kurt Brendlinger, Javier Duarte, Dan Guest, Phil Hebda, Sarah Heim, Liz Hines, Tae Min Hong, Tova Holmes, Brett Jackson, Josh Kunkle, Larry Lee, Chris Lester, Mia Liu, Jonathan Long, Zach Marshall, Chris Meyer, Dominick Olivito, Ryan Reece, Jamie Saxon, Doug Schaefer, Sam Schoenholz, Jon Stahlman, Max Swiatlowski, Emily Thompson, Rami Vanguri, and Keisuke Yoshihara. You are an incredibly smart, generous, and kind group of people, and I'm thankful for the privilege of kicking it with you. Thanks especially to the American expat community at CERN, whose company I've enjoyed for many years. Thanks also to my buds from Duke, including Nim Barshad, Olivia Chang, Felix Ho, Ellie Hwang, Sean McCormack, Luke Medhus, and Kevin Wang, for their outstanding and long-lasting friendship.

Thanks to everyone I lived with as a student, including Kurt Brendlinger, Jamie Saxon, Matt Hickman, Ben Wieder, Javier Duarte, Lawrence Lee, and Phil Hebda. Thanks especially to Kurt for being my housemate for the entirety of grad school and not once strangling me. Thanks to everyone in Philadelphia and Geneva whose couch I have crashed on, including Tae Min Hong, Ellie Hwang, Josh Kunkle, Ryan Reece, Sam Schoenholz, and Keisuke Yoshihara.

Thanks to my family: Claire Tuna, Cari Tuna, Carolyn Hughes, and Ishik Tuna. I try to make you proud every day.

